### 2020-07-01 README.Rmd
documentation changes

The SPSS files in GESIS are not ready for programmatic use in R or for joining into longitudinal panels.

@@

>>>>

The microdata of the European Commissions Eurobarometer surveys are stored and accessible in [GESIS](https://www.gesis.org/home). They are not ready for programmatic use in R or for joining into longitudinal panels. We created this package to help this procedure following the principles of reproducible research.

@@

## Disclaimer

The authors of this package are not affiliated with [GESIS](https://www.gesis.org/home), or the producer of the Eurobarometer surveys, or the European Commission. For more information about the European Commission's Eurobarometer history, visit the European Commission's [Public Opinion](https://ec.europa.eu/commfrontoffice/publicopinion/index.cfm) website.
